\documentclass[11pt]{article}
\usepackage{latexsym}
\oddsidemargin=-0.5cm
\evensidemargin=-0.5cm
\textwidth=17.60cm
\textheight=23.80cm
\topmargin=-1cm
\headsep=1cm

\title{BU CAS CS 525: Compiler Design and Implementation}
\author{(Syllabus)}
\date{}


\begin{document}
\maketitle
\thispagestyle{empty}

\begin{itemize}
\item {\bf Semester} Fall 2022
\item {\bf Instructor}: Hongwei Xi
\item {\bf Lecture Times}: MW 2:30-3:45PM
\item {\bf Classroom}: EOP 264 @ 890 Commonwealth Ave
\item {\bf Reference Book}:\kern6pt
{\em Modern Compiler Implementation in ML} by Andrew W. Appel.  ISBN
0-521-58274-1. Cambridge University Press.
\item {\bf Homepage}:~{\tt http://hwxi.github.io/TEACHING/CS525/2022F}
\item {\bf Overview}:
{\em Compiler Design and Implementation} is a course that introduces
students to some basics in the design and implementation of compilers. In
this course, we are to teach the theory behind various components of a
compiler as well as the programming techniques involved to put the theory
into practice. The chosen programming language for implementation is
ATS. However, you are free to choose another {\em functional} programming
language if you so wish.

\item {\bf Grades}
The final score is calculated using the following formula.
\[\mbox{final score = 40\%$\cdot$(homework) + 20\%$\cdot$(midterm) + 30\%$\cdot$(final) + 10\%$\cdot$(participation)}\]
The final letter grade is calculated as follows.
\begin{itemize}
\item{\bf A}: final score is $80\%$ or above
\item{\bf B}: final score is $70\%$ or above
\item{\bf C}: final score is $60\%$ or above
\item{\bf D}: final score is $50\%$ or above
\end{itemize}

\item {\bf Academic Integrity}:
We adhere strictly to the standard BU guidelines for academic
integrity. For this course, it is perfectly acceptable for you to discuss
the general concepts and principles behind an assignment with other
students. However, it is not proper, without prior authorization of the
instructor, to arrive at collective solutions. In such a case, each student
is expected to develop, write up and hand in an individual solution and, in
doing so, gain a sufficient understanding of the problem so as to be able
to explain it adequately to the instructor.  Under {\em no} circumstances
should a student copy, partly or wholly, the completed solution of another
student. If one makes substantial use of certain code that is not written by
oneself, then the person must explicitly mention the source of the involved
code.

\end{itemize}

\end{document}
